%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Developer Freelancer} % Job title
    {UP AND RUNNING SOFTWARE INC. Iowa} % Organization
    {Remote from Brasov, Romania} % Location
    {Aug. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project \textbf{VTrips.com}: responsible for backend development tasks, focusing on data synchronization and integration across multiple platforms.}
        \item {Data Synchronization: Developed and maintained systems to synchronize data between multiple platforms used by the client, utilizing .NET technologies and Entity Framework to ensure data consistency and integrity.}
        \item {AWS Data Lake Implementation: Played a pivotal role in designing and implementing a centralized data lake on AWS, facilitating efficient data storage and retrieval.}
        \item {ETL Processes with PySpark: Created and managed ETL (Extract, Transform, Load) scripts using Python and PySpark within AWS Glue and Amazon EMR, processing and integrating data from multiple sources into the data lake.}
        \item {Data Pipeline Optimization: Optimized data pipelines for performance and scalability, leveraging AWS services to handle large volumes of data effectively.}
        \item {Project \textbf{Valdi.ai}: worked on an innovative platform focused on distributed machine learning infrastructure.}
        \item {Contributed to the development and evolution of a system enabling customers to run ML models on distributed resources, both on Valdi's and clients' infrastructure.}
        \item {Supported the transition to a novel architecture where customer-provided compute power could be shared and utilized via Docker containers.}
        \item {Involved in Python development, as well as testing and debugging complex distributed Docker-based environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer Freelancer} % Job title
    {RND SOFTWARE DEV S.R.L. Bucharest} % Organization
    {Remote from Brasov, Romania} % Location
    {May. 2019 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for developing and maintaining several components of a complete Internet Filtering Solution}
        \item {User Interface application developed using .NET and WPF technologies}
        \item {Complex Windows Service written in C++, that communicates with the filtering server and the UI}
        \item {Middleware Linux daemon that is responsible for parsing lots of configuration files and keeping a database up-to-date, written in Golang}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer Freelancer} % Job title
    {UP AND RUNNING SOFTWARE INC. Iowa} % Organization
    {Remote from Brasov, Romania} % Location
    {Jul. 2018 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributor to a very interesting project that blends Artificial Intelligence with Blockchain technology.}
        \item {The code base is open to the public on GitHub and it has parts written in C++, functional tests involve some Python code and the UI uses Qt. (projectpai.com)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {SIEMENS INDUSTRY SOFTWARE} % Organization
    {Brasov, Romania} % Location
    {Nov. 2008 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for developing and maintaining a complex application which manages data acquisition and data processing}
        \item {The application, named Test.Lab, is used world wide by important companies from automotive, defense, aviation, energy industry sectors}
        \item {The application is developed under Windows operation system, using C++/C\# technologies. For automation tests purposes Visual Basic and C\# technologies are being used}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {IP DEVEL S.R.L. (PART OF ENEA)} % Organization
    {Bucharest, Romania} % Location
    {Mar. 2007 - Nov. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Embedded Developer for IP cameras from AXIS Communications Sweden. Bug fixes for existent features, maintainance and new firmware releases}
        \item {Linux Ethernet-GSM router (developer) - Architected and implemented a complete software package for a Ethernet-GSM router running Linux}
        \item {The router featured on demand dial-out, dial-in, NAT, dynamic DNS, DNS proxy, VPN, SMS and E-mail based notification and management and a web-based interface with restricted access}
        \item {The challenge in this project was to develop a complete software suite to cover all product requirements and ready for enduser interaction}
        \item {Skills used: Linux, networking, PXA255 (ARM V5TE based processor), PPP, TCP/IP, PHP, modem control}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {RVA LABS S.R.L. (PART OF ISCAN ROBOTICS ISRAEL)} % Organization
    {Bucharest, Romania} % Location
    {Aug. 2005 - Mar. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed automation solutions for Glass Industry}
        \item {Added new features, maintained and commissioned the "Vision" system (written in C++). A system used for error detection on passing glass plates on the production line}
        \item {Involved in four such Vision projects: two in France and two in Romania for Saint Gobain Glass}
        \item {Planned, designed, developed and tested a new computer vision system, written in Delphi/C++, aimed for the detection of the glass ribbon edges and roller marks (resulting from production)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network / System Administrator} % Job title
    {CNDPI ROMSOFT S.A.} % Organization
    {Bucharest, Romania} % Location
    {Mar. 2004 - Aug. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained a Windows based domain through Active Directory Console and its servers: Domain Controllers, DNS, DHCP, SQL Server, Windows Update Server}
        \item {Implemented and managed domain policies}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Developer} % Job title
    {SIMCO INTERNATIONAL S.R.L.} % Organization
    {Bucharest, Romania} % Location
    {Feb. 2002, Jan. 2004} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided software solutions for the Oil Industry}
        \item {Developed a client-server application:
        server written in C running under Linux platform accepting TCP connection from multiple clients, written in Delphi running under Windows platform. The clients provide input data and request the server to perform calculations (www.petroclient.com)}
        \item {Assisted development and tested parts of the web based application www.wellhub.com}
        \item {Developed a client application (in Visual C++ 6.0) for data aquisition and calibration of a "well" monitoring server}
        \item {Implemented a Visual C++ application for data aquisition and storage in different database formats, real time data visualization}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
